UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-08 paper/paper.tex
updates to paper

\subsection{Collect VM usage data}

@@

\subsection{Group usage metrics by machine}

\begin{algorithm}[H]
 \KwData{VM usage data;}
 \KwResult{Metrics containing calculated duration and day;}
 read vmMetrics\;
 \ForAll{line in vmMetrics} {
        calculateDuration();
        calculateDay();
 }
\caption{VM metrics transformation}

\subsection{Calculate number of hours/day, distance from optimality points, CPU and memory utilization}

>>>>

\subsection{Metrics collection}

@@

        8,CPU capacity,FLOAT,YES

        9,Memory capacity,FLOAT,YES

\subsection{Daily metrics aggregation}

\subsubsection{Calculate uptime per machine }
Input: Job start and end time logged for each machine in a form of \textless K, List\textless V\textgreater\textgreater
Output: Uptime based on span between min start time and max end time \textless K,V\textgreater

\subsubsection{Aggregate CPU and memory usage}
Input: Sampled CPU and memory usage logged per job in a form of \textless K, List\textless V\textgreater\textgreater
Output: Aggregated resource usage \textless K,V\textgreater

\subsubsection{Calculate number of jobs per day}
Input: Job id per machine \textless K, List\textless V\textgreater\textgreater
Output: Job count per machine \textless K,V\textgreater

\subsubsection{Calculate cluster averages for aggregations}
Input:
